Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-02-17 paper.tex
fixed underscore bug

        \note{pipeline description}
        A pipeline in PSOM, is a series of connected jobs, which can be
represented as a directed acyclic graph. The pipeline itself is implemented 
using the Matlab/Octave data type. Each job within the pipeline
is assigned a unique name. There is only one mandatory field in the job
description (command). The remaining four optional fields include the list input
files (files_in), the list output files (files_out), the list of files to be
deleted after execution (files_clean) and any Octave or Matlab datatype
containing the remaining parameters necessary for job execution (opt).
Jobs in PSOM run in a protected environment where they only have access to the
parameters that are passed.

        In order to determine whether the opt field was correctly set, the
generic function \textit{psom_struct_defaults} may be applied. This function
will set the default values, ensure all mandatory fields were supplied and issue
warnings for all unidentified attributes.

        To define modules in PSOM, a special Octave/Matlab function type, known as "bricks"
is used. Bricks employ the same parameters as jobs but lack the file_clean
parameter. All bricks contain an opt.flag_test boolean flag, which, if set to
true, allows the user to perform a dry-run of the brick. A dry-run of a brick
consists of updating the default parameters and validating that the brick can
successfully execute with the parameters provided. Bricks also have an option to
specify the output folder (opt.output_folder) for brick outputs to be stored.

        The pipeline generator is an easy way to create complete pipelines with
minimal information provided. A pipeline generator may accept at most the
file_in and opt arguments. It then builds the pipeline based on this
information and the default parameters specified in each brick applied by the
pipeline generator.

@@

>>>>

        \note{pipeline description}
        A pipeline in PSOM, is a series of connected jobs, which can be
represented as a directed acyclic graph. The pipeline itself is implemented 
using the Matlab/Octave data type. Each job within the pipeline
is assigned a unique name. There is only one mandatory field in the job
description (command). The remaining four optional fields include the list input
files (files\_in), the list output files (files\_out), the list of files to be
deleted after execution (files\_clean) and any Octave or Matlab datatype
containing the remaining parameters necessary for job execution (opt).
Jobs in PSOM run in a protected environment where they only have access to the
parameters that are passed.

        In order to determine whether the opt field was correctly set, the
generic function \textit{psom\_struct\_defaults} may be applied. This function
will set the default values, ensure all mandatory fields were supplied and issue
warnings for all unidentified attributes.

        To define modules in PSOM, a special Octave/Matlab function type, known as "bricks"
is used. Bricks employ the same parameters as jobs but lack the file\_clean
parameter. All bricks contain an opt.flag\_test boolean flag, which, if set to
true, allows the user to perform a dry-run of the brick. A dry-run of a brick
consists of updating the default parameters and validating that the brick can
successfully execute with the parameters provided. Bricks also have an option to
specify the output folder (opt.output\_folder) for brick outputs to be stored.

        The pipeline generator is an easy way to create complete pipelines with
minimal information provided. A pipeline generator may accept at most the
file\_in and opt arguments. It then builds the pipeline based on this
information and the default parameters specified in each brick applied by the
pipeline generator.

@@

        To execute a pipeline, the user must provide the pipeline structure and
the pipeline configuration options. The latter consists of the log
directory and the pipepline execution modes (e.g., session, background, batch,
qsub, msub).
